\documentclass[12pt,letterpaper]{article}

%{{{ Package configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Page margin
\usepackage[margin=1in]{geometry}

% Support for bold small cap font
\usepackage[tuenc]{fontspec}
\setmainfont[
    Path=./fonts/,
    Extension=.otf,
    BoldFont=cmu-serif-bold,
    BoldItalicFont=cmu-serif-bold-italic,
    ItalicFont=cmu-serif-italic,
]{cmu-serif}

% Better typesetting quality
\usepackage{microtype}

% Make letter spacing work for both XeLaTeX and LuaLaTeX
\usepackage{ifluatex}
\ifluatex
    \newcommand{\LSSTYLE}{\lsstyle}
\else
    \newcommand{\LSSTYLE}{\addfontfeatures{LetterSpace=12}}
\fi

% Math
\usepackage{amsmath}
\renewcommand{\vec}[1]{\mathbf{#1}}  % Bold as vector

% SI units
\usepackage{siunitx}

% Figure
\usepackage{float,graphicx}

% Redefine section, subsection styles
\usepackage[compact,center,explicit]{titlesec}
\usepackage{textcase}
\titleformat{\section}{\LSSTYLE\normalsize\scshape\filcenter}
    {\thesection}{1em}{\MakeTextUppercase{#1}}
\titleformat{\subsection}{\small\bfseries\filcenter}
    {\thesubsection}{1em}{#1}

% PRL-style horizontal rule
\usepackage{amssymb}
\newcommand{\PRLrule}{
    \bigskip
    \noindent\makebox[\linewidth]{
        \resizebox{0.3333\linewidth}{1pt}{$\blacklozenge$}
    }
    \bigskip
}

% Bold math in section title
\makeatletter
\g@addto@macro\bfseries{\boldmath}
\makeatother

% Set up author affiliation
\usepackage[affil-it]{authblk}

% Set up link, with (hopefully) math symbol support
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\hypersetup{colorlinks,breaklinks,citecolor=blue}
\usepackage{cleveref}

% Set up bibliography
\usepackage[
    %style=phys,
    giveninits=true,
    %backref=true,
    natbib=true,
    backend=biber,
    doi=true,
    % Sort by the order of citation
    sorting=none,
    % This options ensures that no automatic et al. is generated
    %maxbibnames=99,
    % This option must be enabled with 'babel' package
    useprefix=false
]{biblatex}
\addbibresource{umd_phd_candidacy_paper.bib}

%}}}

%{{{ User settings
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% User-defined variables
\def\BaBar/{\textsc{BaBar}}
\def\Y4S/{\ensuremath{\Upsilon(\text{4S})}}
\def\RD/{\ensuremath{\mathcal{R}(D)}}
\def\RDst/{\ensuremath{\mathcal{R}(D^{*})}}
\def\RDDst/{\ensuremath{\mathcal{R}(D^{(*)})}}

% Title info
\title{Review on testing lepton flavor universality in semileptonic channels}
\author{Yipeng Sun}
\affil{Department of Physics, University of Maryland}
\date{\today}

%}}}

\begin{document}
\maketitle

\begin{abstract}
    What is LFUV? (FU physics, FUV physics)
    Why semileptonic decays (good thing about form factor)?
    A historical review, starting from 2012 BaBar;
    Talk about Phoebe's run 1 analyses.
    Talk about what we are doing.
    Talk about expected improvements and drawbacks of our upcoming analysis compared
    to run 1.
\end{abstract}

\section{Introduction}
The Standard Model (SM) has been very successful in describing the interactions
between elementary particles, such as quarks and leptons.
The theory has been tested experimentally to high precision.
However, there are phenomena that cannot be explained by the SM, such as
matter-antimatter asymmetry, hinting for some New Physics (NP) beyond the SM.
One way to search for NP is to measuring the decay rates of certain processes
very precisely;
rates that differ from the SM predictions may provide constraints on NP.

Though experimental discovery, it has been established that leptons have three
flavors:
Charged leptons, namely electron $e$, muon $\mu$, and tauon $\tau$;
their corresponding charge-neutral neutrinos: $\nu_e$, $\nu_\mu$ and $\nu_\tau$.
SM mandates that all three flavors of lepton participate in eletroweak
interaction with the same strength, except for the Higgs mechanism through which
they acquire their mass.
This is known as lepton flavor universality (LFU).

The LFU has been tested in many precision measurements, such as the decay rate
of $K^- \rightarrow e^- \nu_e$ versus $K^- \rightarrow \mu^- \nu_\mu$\footnote{
    Unless specified, charge conjugation is assumed.
}.
So far, no definite violation has been detected.
In this paper, we focus on the semileptonic decay channels of $B$ mesons, such
as $B^- \rightarrow D^{(*)} \l^- \overline{\nu}_l$:
Currently, the world average of the combined decay rate ratios $\RD/$ and
$\RDst/$, defined as\footnote{
    $\mathcal{B}$ denotes branching fraction.
}:
\begin{equation*}
    \RDDst/ \equiv \frac{
        \mathcal{B}\left(
            B^{0,-} \rightarrow D^{+,0(*)} \tau^- \overline{\nu}_\tau
        \right)
    }{
        \mathcal{B}\left(
            B^{0,-} \rightarrow D^{+,0(*)} \mu^- \overline{\nu}_\mu
        \right)
    }
\end{equation*}
has a $3.08\sigma$ deviation from the SM prediction, pointing to a possible
lepton flavor universality violation (LFUV);
many collaborations are working on more precise measurements to provide a
definite answer.

In the rest of the paper, we begin with a theoretical review on
why SM manifests LFU; possible extensions to SM, such as 2-Higgs doublet model
(2HDM), to permit LFUV; and advantages of using semileptonic channels for this
type of measurements.
We then review and compare colliders, such as $e^- e^+$ and hadron collider, and
detectors used in the testing of LFU.
After that, we will review previous experimental results.
Finally, we provide an overlook on updating $\RDDst/$ measurement with LHCb Run
2 data.

\section{Theory}
\subsection{Lepton flavor universality}
\input{include/theories/00-lepton_flavor_universality.tex}

\subsection{Higgs mechanism}

\subsection{Advantages of semileptonic channel decays}

\subsection{2-Higgs doublet models (2HDM)}
% type-II model claimed to be excluded; type-III (very similar to type-II) still
% alive.

\subsection{Leptoquark models}

\section{Review of colliders/detectors used in testing LFU}
The main reason is:
% Initially B factories are meant for CP violation detection.
Initially, detectors of $B$ factories, such as \BaBar/ at PEP-II, were
primarily constructed to for precision measurements on CP violation of $B^0$,
for SM predicts ``large, calculable'' CP violation in the decay of these mesons
\cite{Luth:1994}.
But these detectors proved to be advantageous in the testing of LFU:
These measurements have very similar requirements on the
detector \cite{Boutigny:1995ib}.
Thus, testing of LFU is often part of the secondary goals of these
experiments \cite{Luth:1994}.

In this section, I will review \BaBar/ detector at the PEP-II collider, and LHCb
at the Large Hadron Collider (LHC)---both have conducted various tests on LFU.
These detectors/colliders are representative of the detectors for
electron-position colliders and hadron colliders.

\input{include/detectors/00-babar.tex}
\input{include/detectors/01-lhcb.tex}

\section{Review of previous measurements of \RDDst/}
In this section, I will review some of the more important results of LFU
measurements.
I will focus on \BaBar/ and LHCb results, but related measurement results from
other experiments, such as BELLE, will also be listed.

\input{include/previous_measurements/00-2013_babar_rd_rdstar.tex}
\input{include/previous_measurements/01-2015_lhcb_rdstar.tex}

% 2018 LHCb hadronic decay of Tau -> 3* Pi R(D*)

\section{Outlook for LHCb Run 2 \RDDst/ measurements}
% Expected improvements
% Remember: Run 2 supposedly has better pile-ups.

% Current progress

\PRLrule
\printbibliography
\end{document}
